Rising from the Ashes II.: something something

### 2024-09-02 paper/ms.tex
more serious
Tiny abstract updates

\author{Vadim Semenov}
\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian, Cambridge, MA, USA}

\author{Lars Hernquist}
\affiliation{Center for Astrophysics $|$ Harvard \& Smithsonian, Cambridge, MA, USA}

@@

\begin{abstract}
    The Milky Way is known to host at least two modes in the present day distribution of chemical abundances. The exact cause of this bimodality is disputed, but one class of explanations involves the merger between the Milky Way and a relatively massive sattelite (Gaia-Sausage-Enceladus) at $z\sim2$. However, reproducing this bimodality in simulations is not straightforward, with conflicting results on the prevalance, morphology, and mechanism behind multimodality. We present a case study of a subhalo at $z=1.5$ in the Illustris TNG50 simulation which undergoes a starburst and brief quiescent phase. After a minor post-processing step which boosts the \alphaFe{} of old star particles, we demonstrate that this galaxy hosts a strongly bimodal distribution in the \alphaFe{}-\FeH{} plane. The high- and low-$\alpha$ sequences are neatly separated in time by the brief quiescent period. The quiescent period in this galaxy is not associated with a merger but some unspecified internal process. We argue that the requisite $\alpha$-boosting, post-processing step can be understood as the TNG model underproducing SF in the densest regions at high-$z$.
  \end{abstract}

@@

\subsection{One-Zone Chemical Evolution Model}\label{ssec:onezone_met}
James inserts his bullshit

>>>>

@@

\begin{abstract}
    The Milky Way is known to host at least two modes in the present day distribution of chemical abundances. The exact cause of this bimodality is disputed, but one class of explanations involves the merger between the Milky Way and a relatively massive sattelite (Gaia-Sausage-Enceladus) at $z\sim2$. However, reproducing this bimodality in simulations is not straightforward, with conflicting results on the prevalance, morphology, and mechanism behind multimodality. We present a case study of a galaxy in the Illustris TNG50 simulation which undergoes a starburst and brief quiescent phase. After a minor post-processing step which boosts the \alphaFe{} of old star particles, we demonstrate that this galaxy hosts a strongly bimodal distribution in the \alphaFe{}-\FeH{} plane. The high- and low-$\alpha$ sequences are neatly separated in time by the brief quiescent period. The quiescent period in this galaxy is not associated with a merger but some unspecified internal process which leads to AGN activity. We argue that the post-processing step can be understood as the TNG model underproducing SF in the densest regions at high-$z$.
  \end{abstract}

@@

\subsection{One-Zone Chemical Evolution Model}\label{ssec:onezone_met}
James inserts his section
